---
title: "Atlas of the distribution of skates and rays"
author: "SUMARiS consortium"
date: "December 2018"
output: 
  pdf_document:
    toc: true
    number_section: true
    fig_crop: true
    includes:
      in_header: credo.sty

bibliography: '/home/moi/datahome/work/biblio/enfin/biblioloran.bib'
---

# Framework 

The atlas of the distribution of skates and rays belongs to the work package
(WP) one of the project SUMARiS. 
This WP aims to improve knowledge on rays' fisheries, in support of management
decisions. This atlas is a deliverable of the activity 1.1 of the WP 1.
Data related to skates and rays were collected from differents data providers
and combined in order to map out their spatial distributions.

The atlas of the spatial distribution of the different species of skates and
rays in the Channel and the Southern North Sea is built on historical
data per species and per fishery and information collected during the
project, including reconstructed per-specie catches and landings, and
new information from the fisheries campaigns

This document is a reproducible document: its contents can be updated automatically
according to the arrival of new information. 

```{r global_options, include=T,cache=F,echo=F,warning=F,message=F,progress=F,verbose=F}
#Quarterknitr option
operationnel<-TRUE
knitr::opts_chunk$set(echo=FALSE, 
		      warning=!operationnel, 
		      message=!operationnel,
		      fig.height=8,
		      progress=!operationnel,
		      verbose=!operationnel,
		      include=TRUE,dev='png',autodep=FALSE)
#package
library(COSTcore);library(COSTdbe);library(COSTeda)
library(dplyr);library(tidyr);library(stringr)
library(ggplot2);library(gridExtra)
##library(openxlsx);library(mailR)
library(pander);library(captioner)
library(sf);library(mapdata)
#library(DATRAS)
#library(sparkTable)
#local fct
#source("credo_fct.R")
#initialise les fonctions pour légender tables et figures
tabcap <- captioner(prefix = "Table",level=2)
figcap <- captioner(prefix = "Figure",level=2)

```

```{r data,cache=T}

#load data
cl<-readRDS("cl.rds")
ce<-readRDS("ce.rds")
if(F){
cs<-readRDS("cs.rds")
csuk<-readRDS("csuk.rds")
cs<-rbind2(cs,csuk)
saveRDS(cs,file="csall.rds")
}
cs<-readRDS("csall.rds")
camp<-readRDS("camp.rds")
camp<-camp%>%filter(HaulVal=="V")
camp<-camp%>%filter(CatIdentifier!="-9")
camp<-camp%>%filter(SpecVal!="0")
camp$TotalNo[camp$TotalNo=="-9.00"]<-NA
camp$TotalNo<-as.numeric(camp$TotalNo)
camp0<-readRDS("camp0.rds")
load("codespp.rdata")
codespp<-codespp%>%transmute(taxon=ESPF_COD,spp=ESPF_SCI_LIB,ValidAphiaID=worms,name=ESPF_ENG_LIB,worms)%>%distinct()
#spp correction
#codespp%>%filter(agrepl("acanthias",spp))
#cl ok
#cs
cs@sl$spp[cs@sl$spp=="Raja naevus"]<-"Leucoraja naevus"
cs@hl$spp[cs@hl$spp=="Raja naevus"]<-"Leucoraja naevus"
cs@sl$spp[cs@sl$spp=="Raja"]<-"Rajidae"
cs@hl$spp[cs@hl$spp=="Raja"]<-"Rajidae"
cs@sl$spp[cs@sl$spp=="Leucoraja fullonica"]<-"Raja fullonica"
cs@hl$spp[cs@hl$spp=="Leucoraja fullonica"]<-"Raja fullonica"
cs@sl$spp[cs@sl$spp=="Dipturus batis"]<-"Raja batis"
cs@hl$spp[cs@hl$spp=="Dipturus batis"]<-"Raja batis"
cs@sl$spp[cs@sl$spp=="Leucoraja circularis"]<-"Raja circularis"
cs@hl$spp[cs@hl$spp=="Leucoraja circularis"]<-"Raja circularis"
cs@sl$spp[cs@sl$spp=="Dipturus oxyrinchus"]<-"Raja oxyrinchus"
cs@hl$spp[cs@hl$spp=="Dipturus oxyrinchus"]<-"Raja oxyrinchus"
cs@sl$spp[cs@sl$spp=="Rajella fyllae"]<-"Raja fyllae"
cs@hl$spp[cs@hl$spp=="Rajella fyllae"]<-"Raja fyllae"
cs@sl$spp[cs@sl$spp=="Rostroraja alba"]<-"Raja alba"
cs@hl$spp[cs@hl$spp=="Rostroraja alba"]<-"Raja alba"
cs@sl$spp[cs@sl$spp=="Amblyraja radiata"]<-"Raja radiata"
cs@hl$spp[cs@hl$spp=="Amblyraja radiata"]<-"Raja radiata"
cs@sl$spp[cs@sl$spp=="Torpedo"]<-"Torpedo spp"
cs@hl$spp[cs@hl$spp=="Torpedo"]<-"Torpedo spp"

codespp<-codespp%>%filter(spp!="Leucoraja naevus")%>%mutate(spp=ifelse(spp=="Raja naevus","Leucoraja naevus",spp))

#gearlist
gearlist1<-cl%>%tidyr::separate(foCatEu6,into="gear",sep="_")%>%select(gear)%>%distinct()
gearlist2<-cs@hh%>%tidyr::separate(foCatEu6,into="gear",sep="_")%>%select(gear)%>%distinct()
gearlist<-rbind(gearlist1,gearlist2)%>%distinct()%>%arrange(gear)%>%mutate(gearcat="Other")
gearlist$gearcat[gearlist$gear%in%c("DRB","OTB","OTM","OTT","PS","PTB","PTM","SDN","SSC","TBB")]<-"Trawler"
gearlist$gearcat[gearlist$gear%in%c("FYK","GNC","GND","GNS","GTN","GTR")]<-"Net"
gearlist$gearcat[gearlist$gear%in%c("LHM","LHP","LLD","LLS","LN","LTL")]<-"Line"



#diag spp camp/cl/cs
dcl<-cl%>%group_by(taxon)%>%summarise(w=sum(landWt,na.rm=T)/1000)%>%
	left_join(codespp)%>%ungroup()%>%transmute(taxon,name,spp,worms,w)
dcs<-left_join(left_join(cs@sl,cs@hh),cs@tr)%>%group_by(spp,flag=sampCtry)%>%summarise(wsamp=sum(wt,na.rm=T)/1000,nsamp=n_distinct(paste(trpCode,staNum)))%>%
	ungroup()%>%
	left_join(codespp)%>%ungroup()%>%transmute(taxon,name,spp,worms,flag,nsamp)
dcs<-tidyr::spread(dcs,flag,nsamp,fill=0)
dcamp<-camp%>%group_by(ValidAphiaID,Survey)%>%
	summarise(ncamp=n_distinct(paste(Survey,StNo,HaulNo,Year,Month,Day,TimeShot)),nbind=sum(TotalNo,na.rm=T))%>%
	left_join(codespp)%>%ungroup()%>%select(taxon,name,spp,worms,Survey,ncamp)
dcamp<-tidyr::spread(dcamp,Survey,ncamp,fill=0)

#camp%>%select(Survey,StNo,HaulNo,Year)%>%distinct()%>%dim()

dall<-full_join(full_join(dcl,dcs),dcamp)#%>%arrange(desc(w),desc(nsamp),desc(ncamp))#%>%filter(nsamp>100&!is.na(nbcamp))
#dall%>%filter(is.na(taxon)|is.na(name))
#dall%>%arrange(desc(w))%>%View()
dall<-dall%>%filter(w>2)%>%arrange(desc(w))
#dall%>%View()
#remove strange species


#geography
load("../../data/refTables/geosihsextant/rect.rdata")
load("../../data/refTables/geosihsextant/div.rdata")
#prepa data
listdiv<-c("27.7.d","27.7.e","27.4.b","27.4.c")
div<-div%>%filter(F_DIVISION%in%listdiv)%>%transmute(div=F_DIVISION,label=ETIQUETTE,geometry)
divxy<-st_coordinates(st_centroid(div))
div$x<-divxy[,1]
div$y<-divxy[,2]
#rect<-rect%>%filter(F_DIVISION=="27.7.d")
rect<-rect%>%filter(F_DIVISION%in%listdiv)%>%
	transmute(rect=ICESNAME,div=F_DIVISION,label=ICESNAME,geometry)
rectxy<-st_coordinates(st_centroid(rect))
rect$x<-round(rectxy[,1],3)
rect$y<-round(rectxy[,2],3)

rx<-range(rect$x)
ry<-range(rect$y)

mapbase<-ggplot()+geom_sf(data=div,fill=NA,colour="black",lwd=2)+
    geom_sf(data=rect,fill=NA,alpha=.2)+
    borders("worldHires",xlim=rx,ylim=ry,fill="grey",alpha=.5)+
    geom_sf_label(data=div,aes(label=div))+
    coord_sf(xlim=rx,ylim=ry)+
    theme_bw()+ggtitle("")+xlab("Longitude")+ylab("Latitude")
    #borders("worldHires",xlim=range(status1$x),ylim=range(status1$y),fill="grey")+



```

## Data

Data were collected from three sources: 

- landing: from logbooks and sales notes collected at the national level, the
  landings weights are reported in space and time,
- commercial sampling: fishery catches are sampled at the national level and
  they provide information in weights and size of the catches (landings and
  discards),
- survey sampling: fishery survey provide indices of the species distribution
  (density...), and biological information of the individuals (size, weights,
  sex, maturity). 
  

## Preprocessing

### Data format

Data format follows the DATRAS format [@datras] and the fishframe format [@cost2009].
The metier level 6 have been grouped in 4 categories to simplify the outputs:

- trawler: all the active gears (OTB, PTM, OTT, TBB...),
- net: all the passive gears (GTN, GTR...),
- line: all the gears based on lines and hooks (LHM, LLS...),
- other: all the other gears (MIS, FPO...).


### Data filtering

The time range is fixed to the year 2000 to 2017.
In space, the ICES division on which the data are mapped are the divisions
27.4.b, 27.4.c, 27.7.d and 27.7.e (`r figcap("mapbase",display="cite")`).
Only the rays and skates species are extracted from the different data sources.

```{r mapbase,cache=T,fig.width=5,fig.height=5}
print(mapbase)
```

`r figcap(name="mapbase",caption="area of interest.")`

### Maps

For each species, by data source, a set of map is processed. If no information is available, the related map is empty and contains the message
"no information available".
Data are mapped on the ICES statistical rectangle. The information presented on the map (weights, CPUE...) is aggregated using
the sum or the average of the values in each statistical rectangle. Annual values are aggregated following the same process.
Catch per unit effort are computed using fishing weight divided by the time fishing in hour.

## Data overview

An overview of the data is presented in the `r tabcap("tabbase",display="cite")`.
```{r tabbase}
pander(dall)
```
`r tabcap(name="tabbase",caption="Landing (w, in kg), number of sampling in commercial sampling by country (FRA: France, GB_ENG: England) and 
survey (BTS, FR-CGFS, NS-IBTS) for 2000-2017 by species (taxon: FAO code, name: common name, spp: latin name, worms: worms code).")`

```{r surveypreprocessing,cache=T}
#survey
#c0<-camp%>%filter(ValidAphiaID==105883)%>%mutate(w=as.numeric(CatCatchWgt),x=
#camp$ShootLong<-as.numeric(camp$ShootLong)
#camp$HaulLong<-as.numeric(camp$HaulLong)
#camp$HaulLat<-as.numeric(camp$HaulLat)
#camp$d2<-geosphere::distHaversine(camp[,c("ShootLong","ShootLat")],camp[,c("HaulLong","HaulLat")])
#ggplot(camp%>%filter(HaulLat>0),aes(x=d2,y=Distance))+geom_point()
#plot(as.numeric(camp$Distance),d2)


campsimple<-camp%>%#filter(ValidAphiaID==105883)%>%
	transmute(samp="sci",survey=Survey,id=paste(Survey,Year,StNo,HaulNo),catchCat="SCI",spp=ValidAphiaID,sex=Sex,rect=StatRec,
			 year=Year,month=Month,gear=Gear,
			 x1=as.numeric(ShootLong),y1=as.numeric(ShootLat),
			 x2=as.numeric(HaulLong),y2=as.numeric(HaulLat),
			 d=as.numeric(Distance),l=as.numeric(WingSpread),time=as.numeric(HaulDur),
			 w=as.numeric(CatCatchWgt),n=TotalNo,type=DataType)%>%distinct()
campsimple[campsimple==-9]<-NA
campsimple0<-camp0%>%#filter(ValidAphiaID==105883)%>%
	transmute(samp="sci",survey=Survey,id=paste(Survey,Year,StNo,HaulNo),catchCat="SCI",rect=StatRec,
			 year=Year,month=Month,gear=Gear,
			 x1=as.numeric(ShootLong),y1=as.numeric(ShootLat),
			 x2=as.numeric(HaulLong),y2=as.numeric(HaulLat),
			 d=as.numeric(Distance),l=as.numeric(WingSpread),time=as.numeric(HaulDur))%>%distinct()
campsimple0[campsimple0==-9]<-NA
nbcampspp<-unique(camp$ValidAphiaID)
campsimple1<-campsimple0[rep(seq_len(nrow(campsimple0)),length(nbcampspp)),]
campsimple1$spp<-rep(nbcampspp,each=nrow(campsimple0))
campsimple<-left_join(campsimple1,campsimple)

#missing length
campsimple$d2<-geosphere::distHaversine(campsimple[,c("x1","y1")],campsimple[,c("x2","y2")])
campsimple<-campsimple%>%mutate(d=ifelse(is.na(d),d2,d))%>%select(-d2)
#missing time 
#campsimple%>%tidyr::separate(id,into=c("id0"),sep=" ")%>%group_by(id0=paste(id0,year))%>%summarise(l=mean(l,na.rm=T))%>%View()
#0 in w and n
campsimple$w[is.na(campsimple$w)]<-0
campsimple$n[is.na(campsimple$n)]<-0
#campall<-campsimple%>%group_by(survey,spp,rect,year)%>%summarise(w=mean(w),n=sum(n),time=sum(time))%>%ungroup()%>%left_join(rect)
#campyear<-campsimple%>%group_by(survey,spp,rect,year)%>%summarise(w=mean(w),n=sum(n),time=sum(time))%>%ungroup()%>%left_join(rect)
campallsum<-campsimple%>%group_by(survey,spp,rect)%>%summarise(w=sum(w),n=sum(n),time=sum(time))%>%ungroup()%>%left_join(rect)
campallmean<-campsimple%>%group_by(survey,spp,rect)%>%summarise(w=mean(w),n=mean(n),time=mean(time))%>%ungroup()%>%left_join(rect)
campyearsum<-campsimple%>%group_by(survey,spp,rect,year)%>%summarise(w=sum(w),n=sum(n),time=sum(time))%>%ungroup()%>%left_join(rect)
campyearmean<-campsimple%>%group_by(survey,spp,rect,year)%>%summarise(w=mean(w),n=mean(n),time=mean(time))%>%ungroup()%>%left_join(rect)

```

```{r clpreprocessing,cache=T}
clallsum<-cl%>%
	group_by(country=as.factor(vslFlgCtry),rect,taxon)%>%
	summarise(w=sum(landWt)/1000)%>%ungroup()%>%
	filter(rect!="") %>%left_join(rect)
clallgearsum<-cl%>%tidyr::separate(foCatEu6,into="gear",sep="_")%>%
        left_join(gearlist)%>%
	group_by(country=as.factor(vslFlgCtry),rect,gear=gearcat,taxon)%>%
	summarise(w=sum(landWt)/1000)%>%ungroup()%>%
	filter(rect!="") %>%left_join(rect)
clallyearsum<-cl%>%
	group_by(rect,taxon,year=as.factor(year))%>%
	summarise(w=sum(landWt)/1000)%>%ungroup()%>%
	filter(rect!="") %>%left_join(rect)
clallyeargearsum<-cl%>%tidyr::separate(foCatEu6,into="gear",sep="_")%>%
        left_join(gearlist)%>%
	group_by(country=as.factor(vslFlgCtry),rect,gear=gearcat,taxon,year=as.factor(year))%>%
	summarise(w=sum(landWt)/1000)%>%ungroup()%>%
	filter(rect!="") %>%left_join(rect)
```

```{r cspreprocessing,eval=T}
#quick correction
cs@hh$foDur[cs@hh$foDur<0]<-NA
cs0<-left_join(left_join(cs@sl,cs@hh),cs@tr)%>%
	group_by(country=sampCtry,trpCode,staNum,spp,catchCat,date,year,foCatEu6,rect,x1=lonIni,y1=latIni,x2=lonFin,y2=latFin,foDur)%>%
	summarise(w=sum(wt,na.rm=T))%>%ungroup()
csallmean<-cs0%>%group_by(country=as.factor(country),spp,rect,catchCat=as.factor(catchCat))%>%summarise(w=mean(w)/1000,time=sum(foDur)/60)%>%left_join(rect)
csallyearmean<-cs0%>%group_by(spp,rect,year=as.factor(year))%>%summarise(w=mean(w)/1000,time=sum(foDur)/60)%>%left_join(rect)
csallyeargearmean<-cs0%>%
	tidyr::separate(foCatEu6,into="gear",sep="_")%>%
        left_join(gearlist)%>%
	group_by(spp,rect,year=as.factor(year),gear=gearcat)%>%summarise(w=mean(w)/1000,time=sum(foDur)/60)%>%left_join(rect)


if(F){
#x11(h=4)
#pipo<-campall%>%filter(spp=={{worms}})
pipo<-csallyearmean%>%filter(spp=="Raja clavata")
aa<-ggplot()+
    geom_raster(data=pipo,aes(x=x,y=y,fill=w),stat="identity",alpha=1) +
    scale_fill_distiller(palette='Spectral',name="CPUE\n(tons)",trans="log10")+
    borders("world",xlim=rx,ylim=ry,fill="grey",colour=NA,alpha=1)+
    coord_quickmap(xlim=rx,ylim=ry)+
    facet_wrap(~year,drop=F)+
    theme_bw()+ggtitle("Landings: {{spp}}")+xlab("Longitude")+ylab("Latitude")

}


```



```{r testarea,eval=F,include=F}
if(F){
#survey1
#x11(h=4)
#pipo<-campall%>%filter(spp=={{worms}})
pipo<-campallmean%>%filter(spp==105883)
uu<-ggplot()+
    geom_raster(data=pipo,aes(x=x,y=y,fill=(w/1000)/(time/60)),stat="identity",alpha=1,colour="black")+
   #geom_sf(data=div,fill=NA,colour="black",lwd=1)+
    scale_fill_distiller(palette='Spectral',name="CPUE\n(kg.h-1)",trans="log10")+
    #geom_sf(data=rect,fill=NA,alpha=1,lwd=.1)+
    borders("world",xlim=rx,ylim=ry,fill="grey",colour=NA,alpha=1)+
    #geom_sf_label(data=div,aes(label=div))+
    #coord_sf(xlim=rx,ylim=ry)+
    coord_quickmap(xlim=rx,ylim=ry)+
    facet_wrap(~survey)+
    theme_bw()+ggtitle("{{spp}}")+xlab("Longitude")+ylab("Latitude")

#pipo<-campall%>%filter(spp=={{worms}})
pipo<-campyearmean%>%filter(spp==105883&survey=="BTS")
#x11(w=8,h=10)
aa<-ggplot()+#geom_sf(data=div,fill=NA,colour="black",lwd=2)+
    geom_raster(data=pipo,aes(x=x,y=y,fill=(w/1000)/(time/60)),stat="identity",alpha=1)+
    facet_wrap(~year,ncol=4)+
    scale_fill_distiller(palette='Spectral',name="CPUE\n(kg.h-1)",trans="log10")+
    #geom_sf(data=rect,fill=NA,alpha=.2,lwd=.1)+
    #borders("worldHires",xlim=rx,ylim=ry,fill="grey",colour=NA,alpha=1)+
    borders("world",xlim=rx,ylim=ry,fill="grey",colour=NA,alpha=1)+
    #geom_sf_label(data=div,aes(label=div))+
    #coord_sf(xlim=rx,ylim=ry)+
    coord_quickmap(xlim=rx,ylim=ry)+
    theme_bw()+ggtitle("BTS: {{spp}}")+xlab("Longitude")+ylab("Latitude")
pipo<-campallmean%>%filter(spp==105711)#%>%filter(w==0)
plt<-ggplot()+#geom_sf(data=div,fill=NA,colour="black",lwd=2)+
    geom_raster(data=pipo,aes(x=x,y=y,fill=(w/1000)/(time/60)),stat="identity",alpha=1)+
    borders("world",xlim=rx,ylim=ry,fill="grey",colour=NA,alpha=1)+
    coord_quickmap(xlim=rx,ylim=ry)+
    facet_wrap(~survey,drop=FALSE)+
    theme_bw()+ggtitle("Rajidae")+xlab("Longitude")+ylab("Latitude")

    plt+scale_fill_distiller(palette='Spectral',name="CPUE\n(kg.h-1)",trans="log10")
}
```


\newpage


```{r chapter0}
    rmd1<-knitr::knit_expand("expand_atlas.Rmd", spp = dall$spp[1],worms=dall$worms[1],taxon=dall$taxon[1])
    rmd<-rmd1
    for(i in 2:nrow(dall)){
      rmdtmp<-knitr::knit_expand("expand_atlas.Rmd", spp = dall$spp[i],worms=dall$worms[i],taxon=dall$taxon[i])
      rmd<-paste(rmd,rmdtmp,collapse="\n")
    }
    #for(i in 
    #rmd2<-knitr::knit_expand("expand_atlas.Rmd", spp = dall$spp[10],worms=dall$worms[10],taxon=dall$taxon[10])
    #rmd3<-knitr::knit_expand("expand_atlas.Rmd", spp = dall$spp[2],worms=dall$worms[2],taxon=dall$taxon[2])
    #rmd<-paste(rmd1,rmd2,collapse="\n")
    #rmd<-rmd1

    #cat(rmd)
#pipo<-data.frame(a="a",b="b")
#rmd <- sapply(
#  dall,
#  function(pipo) {
#    knitr::knit_expand("expand_atlas.Rmd", spp = pipo[3],worms=pipo[4])
#  }
#)

#sapply(list(1:3,5:6,function(i,j){ knitr::knit_expand(text=c("## {{spp}} {{aka}}"),spp=i,aka=j)})

#rmd <- paste(rmd, collapse = "\n")
#cat(rmd)
``` 

```{r rendertruc,results = "asis"}
rendered <- knitr::knit(text = rmd, quiet = TRUE)
cat(rendered, sep = "\n")
``` 

\newpage

# Bibliography

